On Secure Delegation of SampBQP with a Classical Client

### 2020-02-06 preliminaries.tex
Make editorial pass
Make editorial changes and add more TODOs
Add TODO to define complexity classes
Fix missing dfns

@@

\hannote{sampling generalize decision blah} \Ethan{That doesn't sound right}

@@

There are many formulations of quantum de Finetti theorems. We use the one from \cite{Brandão2017} because we need logarithmic dependence on $|A|$.
\begin{thm}
	\label{deFinetti}
	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state. Then for every $0\leq l\leq k$ there exists states $\set{\rho_i}$ and $\set{p_i}\subset\bbR$ such that
	$$\max_{\Lambda_1,\ldots,\Lambda_l}\norm{(\Lambda_1\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\sum_ip_i\rho_i^{A_1}\otimes\ldots\otimes\rho_i^{A_l}\right)}_1\leq\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$$
\end{thm}

@@

We use the quantum fully homomorphic encryption scheme given in \cite{mahadev_qfhe} which is compatible with our use of a classical client. We start by presenting the interface of a homomorphic encryption scheme:

\begin{dfn}
	A leveled homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{HE.Keygen}(1^\lambda, 1^L)\rightarrow(pk, evk, sk)$
		\item $\mathsf{HE.Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{HE.Dec}_{sk}(c)\rightarrow \mu^*$
		\item $\mathsf{HE.Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}

>>>>

\subsection{Relevant complexity classes}

We define a few relevant complexity classes. \Ethan{Do we need to define $\BPP$ and $\BQP$ too?}

\begin{dfn}
	$\QMA$ is the quantum analogue of the class $\MA$. The verifier in $\QMA$ is now a $\BQP$ machine.
\end{dfn}

\begin{dfn}
	$\FBQP$ is the functional analogue of the class $\BQP$. That is, every instance corresponds to a string rather than a yes/no bit. The error probability is still bounded above away from $\fot$ for some uniform quantum circuit family.
\end{dfn}

@@

@@

De Finetti theorem provides a way to obtain close to independent samples by taking random subsystems of a quantum system.
There are many formulations; we use the one from \cite{Brandão2017} because we need logarithmic dependence on $|A|$.
\begin{thm}
	\label{deFinetti}
	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state. Then for every $0\leq l\leq k$ there exists states $\set{\rho_i}$ and $\set{p_i}\subset\bbR$ such that
	$$\max_{\Lambda_1,\ldots,\Lambda_l}\norm{(\Lambda_1\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\sum_ip_i\rho_i^{A_1}\otimes\ldots\otimes\rho_i^{A_l}\right)}_1\leq\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$$
\end{thm}

@@

We use the quantum fully homomorphic encryption scheme given in \cite{mahadev_qfhe} which is compatible with our use of a classical client. We start by presenting the interface of a homomorphic encryption scheme:
\begin{dfn}
	A leveled homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{HE.Keygen}(1^\lambda, 1^L)\rightarrow(pk, evk, sk)$
		\item $\mathsf{HE.Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{HE.Dec}_{sk}(c)\rightarrow \mu^*$
		\item $\mathsf{HE.Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}
